---
template_version: "1.0"
template_type: "lab"
template_description: "R lab exercise template with code scaffolding"
template_variables: [WEEK, TOPIC, COURSE, DATE, INSTRUCTOR]
---
---
title: "Lab {{WEEK}}: {{TOPIC}}"
subtitle: "{{COURSE}}"
author: "{{INSTRUCTOR}}"
date: "{{DATE}}"
format:
  html:
    toc: true
    code-fold: false
    code-tools: true
execute:
  echo: true
  warning: false
  message: false
---

## Overview

**Objectives:**

1.
2.
3.

**Prerequisites:**

- Completed Week {{WEEK}} lecture
- R and RStudio installed
- Required packages: tidyverse, ggplot2

## Setup

```{r}
#| label: setup
#| message: false

# Load required packages
library(tidyverse)
library(ggplot2)

# Set seed for reproducibility
set.seed(545)
```

## Part 1: Data Exploration

### Exercise 1.1



```{r}
#| label: exercise-1-1

# Your code here

```

### Exercise 1.2



```{r}
#| label: exercise-1-2

# Your code here

```

## Part 2: Analysis



### Exercise 2.1



```{r}
#| label: exercise-2-1

# Your code here

```

## Part 3: Interpretation

### Questions

1.

2.

3.

## Submission

- Complete all exercises
- Render to HTML
- Submit via Canvas by [deadline]
