---
template_version: "1.0"
template_type: "slides"
template_description: "RevealJS slides template for lectures"
template_variables: [WEEK, TOPIC, COURSE, DATE, INSTRUCTOR]
---
---
title: "{{TOPIC}}"
subtitle: "Week {{WEEK}} - {{COURSE}}"
author: "{{INSTRUCTOR}}"
date: "{{DATE}}"
format:
  revealjs:
    theme: default
    transition: fade
    slide-number: true
    chalkboard: true
    footer: "{{COURSE}} | Week {{WEEK}}"
execute:
  echo: true
  warning: false
---

# {{TOPIC}} {background-color="#003366"}

## Learning Objectives

1.
2.
3.

## Outline

- Section 1
- Section 2
- Section 3
- Summary

# Section 1 {background-color="#336699"}

## Key Concept

::: {.incremental}
- Point 1
- Point 2
- Point 3
:::

## Example

```{r}
#| echo: true
#| eval: true

# Example code
```

## Visual

```{r}
#| echo: false
#| fig-width: 8
#| fig-height: 5

# Visualization code
```

# Section 2 {background-color="#336699"}

## Main Points

::: {.columns}
::: {.column width="50%"}
**Left Column**

- Item 1
- Item 2
:::
::: {.column width="50%"}
**Right Column**

- Item 1
- Item 2
:::
:::

# Summary {background-color="#003366"}

## Key Takeaways

1.
2.
3.

## Next Week

- Preview of upcoming topics

## Questions?

::: {.callout-note}
Office hours: [Day/Time]
:::
